Seismic Hazard Estimation of Northern Iran Using Smoothed Seismicity

### 2016-07-08 main.tex
completed first revision of abstract
changed references filename and made modifications to notes about the 2016 paper
looks like done

% Packages
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{marvosym}

@@

% Authors
\author{%
	N.~Khoshnevis \and
	S.~Azizzadeh-Roodpish \and
	R.~Taborda \and
	C.~H.~Cramer
}

% Affiliations
\institute{%
	N.~Khoshnevis \and C.~H.~Cramer \at
	Center for Earthquake Research and Information,
	University of Memphis, 3890 Central Ave., Memphis TN 38152, USA\\
	\and
	S.~Azizzadeh-Roodpish \and R.~Taborda (\Letter)\at
	Department of Civil Engineering, and
	Center for Earthquake Research and Information,
	University of Memphis, 3890 Central Ave., Memphis TN 38152, USA\\
	\email{ricardo.taborda@memphis.edu}  
}

@@

% Bibliography
\bibliographystyle{spbasic}
\bibliography{PSHA}
% \nocite{*}

>>>>

% Packages
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{marvosym}
\usepackage{textcomp}

@@

% Authors
\author{%
	N.~Khoshnevis \and
	R.~Taborda \and
	S.~Azizzadeh-Roodpish \and
	C.~H.~Cramer
}

% Affiliations
\institute{%
	N.~Khoshnevis \and C.~H.~Cramer \at
	Center for Earthquake Research and Information,
	University of Memphis, 3890 Central Ave., Memphis TN 38152, USA\\
	\and
	R.~Taborda (\Letter) \and S.~Azizzadeh-Roodpish \at
	Department of Civil Engineering, and
	Center for Earthquake Research and Information,
	University of Memphis, 3890 Central Ave., Memphis TN 38152, USA\\
	\email{ricardo.taborda@memphis.edu}  
}

@@

% Bibliography
\bibliographystyle{spbasic}
\bibliography{references}
% \nocite{*}
